\documentclass[10pt]{article}
\usepackage{amsmath,amssymb,amsthm}

% enumitem package for easy control of spacing around and in lists
\usepackage{enumitem}

% todonotes package for making comments
\usepackage[textwidth=4cm,textsize=small,shadow]{todonotes}
\newcommand{\answerbox}[1]{\todo[inline,author={Kartik},color=lightgray,size=normalsize]{#1}}
\newcommand{\marginbox}[1]{\todo[color=green,size=small]{#1}}

% package amsrefs to make citations
\usepackage{amsrefs}

% geometry package for setting nonstandard margins
\usepackage[letterpaper,right=6cm,left=2cm]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ...

% for proper formatting of programs
\usepackage{listings}

%hyperref package for adding hyperlinks
\usepackage{hyperref}

% fancy math notation for important sets
\newcommand{\NN}{\ensuremath{\mathbb N}}
\newcommand{\ZZ}{\ensuremath{\mathbb Z}}
\newcommand{\QQ}{\ensuremath{\mathbb Q}}
\newcommand{\RR}{\ensuremath{\mathbb R}}
\newcommand{\TT}{\ensuremath{\mathbb T}}
\newcommand{\CC}{\ensuremath{\mathbb C}}
\newcommand{\FF}{\ensuremath{\mathbb F}}
\newcommand{\cA}{\ensuremath{\cal A}}

\newtheorem{theorem}{Theorem} %[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{claim}{Claim}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{conjecture}[theorem]{Conjecture}

\begin{document}
\title{MTH370: Homework Set \#1}
\author{Kartik Kumar}
\date{September 6th, 2023}
\maketitle

You should attempt each of these problems, and write your solution using \LaTeX as best as you are able. Exchange files with your partner on Saturday, September 2: not before and not after! Then, with your partner, produce a single \LaTeX file that has your combined best work, print out the PDF, and hand the PDF to your professor on Wednesday, September 6. Give the source file the name ``hw1-partner1-partner2.tex'', and email it to Prof O'Bryant with the subject line ``MTH370 HW1''.

You should keep both your and your partner's separate versions, and your combined version.

\begin{enumerate}[noitemsep]
    \item Get access to \LaTeX\ and compile this document. That may involve installing it on a personal machine, but these days the easiest way is to set up a free account on \href{http://www.overleaf.com}{Overleaf}. Then look through the header. Change the author to your name, and change the date to the due date for this assignment, September 6, 2023. How did you get access to \LaTeX?
        \answerbox{I went to Overleaf.}
    \item Get access to Python. For most of you, this means installing it and VSCode on your personal machines. I'm open to other solutions.
        \begin{enumerate}
            \item How did you get access to Python?
                \answerbox{I access Python through the local runtime on my machine.
                \newline 1. Download Python runtime installer from website.
                \newline 2. Install the Python Tools extension for VSCode
                \newline 3. Write Python code using VSCode
                \newline 4. Execute Python through the commmand line using "python file.py"}
            \item The following code implements a factorial function.
\lstset{language=Python,caption={Python Code for Factorial},frame=single}
            \begin{lstlisting}
def factorial_recursive(n):
    if n == 0 or n == 1:
        return 1
    else:
        return n * factorial_recursive(n - 1)

# Test the function
num = int(input("Enter a number: "))
result = factorial_recursive(num)
print(f"The factorial of {num} is {result}")
            \end{lstlisting}
            Use it to compute $100!$. What is the largest $n$ for which \emph{you} can compute $n!$ in under $1$ minute?
            \answerbox{The factorial of 100 is:
            \newline9332621544394415268169923885626670049
            \newline071596826438162146859296389521759999322991560894146
            \newline3976156518286253697920827223758251185210916864000000000000000000
            \newline000000}
            \lstset{language=Python,caption={Python Code for Largest Factorial In 1 Minute},frame=single}
            \begin{lstlisting}
import sys
import time

# We need to do this because output factorial is very large
sys.set_int_max_str_digits(100000000)

n = 0
factorial = 1
start_time = time.time()

while True:
    # Base factorial case
    if n == 0 or n == 1:
        factorial = 1
    else:
        factorial *= n

    # Increment the number
    n += 1

    # Check elapsed time after each iteration
    if time.time() - start_time > 60:
        break

# Print the result
print(f"Largest computable factorial in under 1 minute: {n - 1}!")
print(f"Time elapsed: {time.time() - start_time} seconds")
print(f"{n - 1}! = a number that is {len(str(factorial))} digits long")
            \end{lstlisting}
            \answerbox{\newline Largest computable factorial in under 1 minute: 490409!
\newline Time elapsed: 60.000478744506836 seconds
\newline 490409! = a number that is 2577723 digits long\newline\newline Note! This was calculated on an i9-10850k @ 4.8 Ghz with 32 GB Memory.}
        \end{enumerate}
    \item Write the following complex numbers in cartesian form, i.e., as $a+bi$ with $a,b$ real.
        \begin{enumerate}
            \item $\cos(\pi/3)+i \sin(\pi/3) +\frac{1}{\sqrt2}-3i$
            \answerbox{$\frac{1+\sqrt{2}}{2}+\frac{-6+\sqrt{3}}{2}i$}

            \item $(5-2i)(3+3i)$
            \answerbox{$21+9i$}

            \item $(5-2i)^4$
            \answerbox{$41-840i$}

            \item $\displaystyle \frac{5-2i}{3+i}$
            \answerbox{$\frac{13}{10}-\frac{11}{10}i$}
        \end{enumerate}
    \item Write the following dual numbers in cartesian form, i.e., as $a+b\varepsilon$ with $a,b$ real.
    \begin{enumerate}
        \item $\cos(\pi/3)+\varepsilon \sin(\pi/3) +\frac{1}{\sqrt2}-3\varepsilon$
        \answerbox{$\frac{1+\sqrt{2}}{2}+\frac{-6+\sqrt{3}}{2}\varepsilon$}

        \item $(5-2\varepsilon)(3+3\varepsilon)$
        \answerbox{$15+9\varepsilon$}

        \item $(5-2\varepsilon)^4$
        \answerbox{$625-1000\varepsilon$}

        \item $\displaystyle \frac{5-2\varepsilon}{3+\varepsilon}$
        \answerbox{$\frac{15}{9}-\frac{11}{9}\varepsilon$}

        \item $\sin(2+5\varepsilon)$
        \answerbox{$\sin(2)+5\cos{2} \varepsilon$}

        \item $\displaystyle \left(\frac{\cos \left(e^{2+\varepsilon}\right)}{2+\varepsilon+2}\right)^2+\sin (2+\varepsilon) e^{-\sin (2+\varepsilon)}$
        \answerbox{Confused}

    \end{enumerate}
    \item Explain how to use calculus and Newton's Method to find the maximum value of $$f(x)=\left(\frac{\cos \left(e^x\right)}{x+2}\right)^2+\sin (x) e^{-\sin (x)}$$ on $[0,2]$, correct to $4$ digits. If you have to pay \$1 each time you evaluate $\sin,\cos,\exp$ (at any nontrivial value), how expensive will your solution be?

    One way to do this problem, were it important, would be to just ask Wolfram$\mid$Alpha. But at this point, we are more interested in building the muscles needed to attack harder problems, and to understand which problems machines can handle and on which problems they become untrustworthy.

    \begin{enumerate}
    \item First, compute the first derivative \(f'(x)\) of the function. This will involve using the chain rule, product rule, and quotient rule of differentiation.
    \item Set \(f'(x) = 0\) to find the critical points within the interval [0,2].
    \item Use Newton's method to approximate the roots of \(f'(x) = 0\). Start with an initial guess, say \(x_0\), within the interval. Then, iteratively apply the formula:
    \[ x_{n+1} = x_n - \frac{f'(x_n)}{f''(x_n)} \]
    until the difference between successive approximations is small or until we have reached a desired accuracy.
    \item Compute the second derivative \(f''(x)\) to determine the nature of each critical point. If \(f''(x) > 0\), then \(f(x)\) has a local minimum at that point. If \(f''(x) < 0\), then \(f(x)\) has a local maximum.
    \item Evaluate the function \(f(x)\) at the critical points and the endpoints of the interval [0,2] to determine the maximum value on the interval.
    \item Keep track of the number of times we evaluate \(\sin\), \(\cos\), and \(\exp\) to determine the total cost.
\end{enumerate}
\end{enumerate}

\end{document}
